### 2013-02-16 doc/icml2013/regression.tex

\paragraph{Low-rank regression}
%\label{sec:regression}

We now bound the error of
the compound parameter estimates,
$\|\Delta_2\|_F^2$ and $\|\Delta_3\|_F^2$,
where $\Delta_2 \eqdef \hat M_2 - M_2$
and $\Delta_3 \eqdef \hat M_3 - M_3$.

>>>>

\paragraph{Low-rank regression}
%\label{sec:regression}
\vspace{-0.5em}
We now bound the error of
the compound parameter estimates,
$\|\Delta_2\|_F^2$ and $\|\Delta_3\|_F^2$,
where $\Delta_2 \eqdef \hat M_2 - M_2$
and $\Delta_3 \eqdef \hat M_3 - M_3$.
